ManuscriptFigures

### 2024-03-01 Code/ManuscriptFigures.Rmd
Changed red light to lighter shade

MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(450))

@@

MyWavelengths = c("WW", 660, 450)
OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))

names(OverlayColours) <- MyWavelengths
OverlayColours

@@

        axis.text = element_text(size = 15, color = "black"))

@@

TEST <- PURPARFits %>% 
  filter(Strain == "MED4", WL == 660, )

>>>>

MCMIXColours = c("black", "#f40d30", w_length2rgb(450))

@@

@@

        axis.text = element_text(size = 15, color = "black"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@
